---
title: "Errata for *Persuasion in Parallel*"
format:
  pdf:
    output-file: coppock_2022_errata.pdf
    geometry: margin=1.25in
    fontsize: 11pt
---

```{r}
#| label: setup
#| include: false
library(here)
library(tidyverse)

here::i_am("errata.qmd")

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

out <- function(file) {
  read_csv(here::here("maintained", "output", file), show_col_types = FALSE)
}

one_dp <- function(x) sprintf("%.1f", x)
two_dp <- function(x) sprintf("%.2f", x)

# Entry 1: the two study rows of table 2.2, whose labels are interchanged.
table_2.2 <- out("table_2.2_lrl_reanalysis.csv")
lrl_cell <- function(content_label, panel, group) {
  row <- table_2.2 |>
    filter(content_factor == content_label, outcome_variable == panel)
  stopifnot(nrow(row) == 1)
  one_dp(row[[paste("Capital Punishment", group)]])
}
pro_study <- function(panel, group) lrl_cell("After pro capital punishment study", panel, group)
anti_study <- function(panel, group) lrl_cell("After anti capital punishment study", panel, group)

# Entry 2: chapter 6's prose against the chapter 6 tables it describes. The corrected
# figures are the book's own printed cells, read from the transcription rather than from a
# run, because the estimator behind them has no seed.
published_maintext <- read_csv(here::here("ground_truth", "published_maintext_tables.csv"),
                               show_col_types = FALSE)
seed_dispersion <- read_csv(here::here("ground_truth", "seed_dispersion.csv"),
                            show_col_types = FALSE)
printed_pct <- function(float, panel_label, row) {
  cell <- published_maintext |>
    filter(table == float, panel == panel_label, row_label == row)
  stopifnot(nrow(cell) == 1)
  sprintf("%.0f", 100 * as.numeric(cell$value_paper))
}
c6 <- tribble(
  ~float,      ~panel,     ~row_label,                       ~quantity,                        ~in_prose,
  "table_6.2", "estimate", "Prediction: weaker persistence", "Prediction: weaker persistence", 0.20,
  "table_6.3", "10 days",  "Overall",                        "Overall, 10 days",               0.46,
  "table_6.3", "30 days",  "Overall",                        "Overall, 30 days",               0.44,
  "table_6.3", "10 days",  "Republican",                     "Republican, 10 days",            0.57,
  "table_6.3", "10 days",  "Democrat",                       "Democrat, 10 days",              0.43
) |>
  left_join(published_maintext |> select(float = table, panel, row_label, in_table = value_paper),
            by = c("float", "panel", "row_label")) |>
  left_join(seed_dispersion, by = c("float", "quantity")) |>
  mutate(table_inside = in_table >= minimum - 1e-9 & in_table <= maximum + 1e-9,
         prose_inside = in_prose >= minimum - 1e-9 & in_prose <= maximum + 1e-9)
stopifnot(nrow(c6) == 5, !any(is.na(c6$in_table)), !any(is.na(c6$minimum)),
          all(c6$table_inside), !any(c6$prose_inside), n_distinct(c6$n_seeds) == 1)
c6_seeds <- unique(c6$n_seeds)

# Entry 3: the Hiscox expert cue persistence estimates.
table_6.4 <- out("table_6.4_all_persistence.csv")
hiscox <- function(sample_label) {
  row <- table_6.4 |>
    filter(str_starts(study_label, "Hiscox"), Sample == sample_label,
           Treatment == "Expert cue")
  stopifnot(nrow(row) == 1)
  100 * as.numeric(str_extract(row$`Persistence Ratio`, "^[-0-9.]+"))
}
hiscox_mturk <- round(hiscox("MTurk"))
hiscox_gfk <- round(hiscox("GfK"))

# Entry 4: the convincingness ratings in the lower half of table 2.3.
convincing <-
  out("table_2.3_gc_replication.csv") |>
  filter(rating == "convincing", str_detect(predisposition, "Proponents"))
stopifnot(nrow(convincing) == 1)

# Entry 5: the standard error of the two-sided effect on support among opponents.
two_sided_se <-
  out("figure_5.17_gc_pro_con_effects.csv") |>
  filter(dv == "support_recode_change", term == "Pro Con",
         predisposition == "Capital Punishment Opponents")
stopifnot(nrow(two_sided_se) == 1)
```
```{r}
#| label: entries
#| include: false

# THE ERRATA SPINE. Every entry is defined once, here, and rendered from this tibble into
# this document and into the machine-readable errata_entries.csv written at the bottom of
# the file, which is what any other document carrying these corrections reads. Before the
# spine existed an entry was written out in prose wherever it was needed, and the copies
# had already diverged.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here. Nothing else in a field is markup, so the same string can be set by any of them.
#
# Numbering is the published note's and is APPEND-ONLY: entry 3 can already have been cited,
# so a later finding is added at the end and never interleaved.
#
# A published or corrected value that the pipeline settles stays computed: the field is built
# with str_glue() so the number is produced when this document renders, not typed. Entry 2 is
# the exception the estimator forces, and it is computed too: its corrected figures are the
# book's own printed cells, read at render time from the transcription of the tables rather
# than from a run, because the bootstrap behind them has no seed.
#
# Entries 1 and 2 carry more than one changed artifact. Their published and corrected fields
# hold one paragraph per artifact, in printed order, separated by a blank line; the two
# entries' floats and page headings stay in the document below, because they are presentation
# rather than spine.
#
# claim_ids is the semicolon-separated list of ground-truth claim_id values the entry
# corrects, and it is what makes "is this finding published?" a query rather than a reading
# of every note. It is empty where an entry has no ground-truth row, which is normal for a
# bibliographic or structural entry. ground_truth/build_ground_truth.R refuses to build if
# any id here is absent from the ground truth.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "label", "pipeline", "brief",
  "In table 2.2 (p. 26), the two study rows carry each other's labels, in both panels.",
  "published table 2.2, p. 26",
  paste("After [[pro]]-capital punishment study",
        "After [[anti]]-capital punishment study", sep = "\n\n"),
  paste("After [[anti]]-capital punishment study",
        "After [[pro]]-capital punishment study", sep = "\n\n"),
  str_glue(
    "The changed artifact is the two labels alone. Every value is correct, and the rows are ",
    "in the order the analysis produces them, whose study-content factor runs con before pro ",
    "and so puts the anti-capital punishment study first. Figure 2.2, printed on the same ",
    "page from the same variable, shows the con study at ",
    "{anti_study('attitude', 'Proponents')} for proponents and ",
    "{anti_study('attitude', 'Opponents')} for opponents and the pro study at ",
    "{pro_study('attitude', 'Proponents')} and {pro_study('attitude', 'Opponents')}, which is ",
    "the table's two rows the other way up. The sentence beneath the figure, reporting that ",
    "self-assessed change is higher in the pro condition than in the null and higher in the ",
    "null than in the con, says the same thing again. The \"Combined\" rows are sums of the ",
    "two and are unaffected, as is the reading of the table that the surrounding text draws ",
    "from them."),
  "t2_2_row_labels",

  2, "quantity", "pipeline", "full",
  "Four sentences in chapter 6 report persistence figures that the chapter's own tables print differently.",
  "published pp. 114 and 117--118",
  paste(
    "Across all 12 studies, the average persistence ratio was about one-third, or 34 percent; that figure is 50 percent in the stronger persistence group and [[20]] percent in the weaker persistence group (see table 6.2).",
    "After ten days treatment effects decay to [[46]] percent (SE = 5 percent) of their original magnitudes.",
    "After thirty days, average persistence declines to [[44]] percent (SE = 6 percent).",
    "For Republicans, persistence after ten days averaged [[57]] percent; this figure was [[43]] percent for Democrats.",
    sep = "\n\n"),
  paste(
    str_glue("Across all 12 studies, the average persistence ratio was about one-third, or 34 percent; that figure is 50 percent in the stronger persistence group and [[{printed_pct('table_6.2', 'estimate', 'Prediction: weaker persistence')}]] percent in the weaker persistence group (see table 6.2)."),
    str_glue("After ten days treatment effects decay to [[{printed_pct('table_6.3', '10 days', 'Overall')}]] percent (SE = 5 percent) of their original magnitudes."),
    str_glue("After thirty days, average persistence declines to [[{printed_pct('table_6.3', '30 days', 'Overall')}]] percent (SE = 6 percent)."),
    str_glue("For Republicans, persistence after ten days averaged [[{printed_pct('table_6.3', '10 days', 'Republican')}]] percent; this figure was [[{printed_pct('table_6.3', '10 days', 'Democrat')}]] percent for Democrats."),
    sep = "\n\n"),
  paste(
    "The page 118 sentence is the one that moves furthest, and the two halves fail",
    "differently. Its 57 percent is table 6.3's Republican estimate after *thirty* days, read",
    "one column across from the ten-day estimate the sentence describes; its 43 percent is no",
    "cell of the table at all. The sentence that follows, that the Republican and Democratic",
    "estimates are not statistically significantly different, is unaffected and holds on the",
    "corrected figures, which are closer together than the published pair. The standard errors",
    "on page 117 are left as printed. The ten-day one agrees with table 6.3; the thirty-day one",
    "says 6 percent where the table prints 0.05, but the reanalysis returns 6 percent as well,",
    "so that figure sits inside the bootstrap's noise in a way none of the five estimates above",
    "does. Tables 6.2 and 6.3 are otherwise correct as printed and are not reprinted here."),
  paste("c6_persistence_weaker", "c6_oped_ten_days", "c6_oped_thirty_days",
        "c6_oped_rep_ten_days", "c6_oped_dem_ten_days", sep = ";"),

  3, "label", "pipeline", "full",
  "Page 114 attributes a persistence estimate to a sample that is not in the persistence analysis.",
  "published p. 114",
  str_glue("Curiously, the different replications of the Hiscox (2006) \"expert\" treatment generated very different persistence estimates: {hiscox_mturk} percent on MTurk but {hiscox_gfk} percent on [[Lucid]]."),
  str_glue("Curiously, the different replications of the Hiscox (2006) \"expert\" treatment generated very different persistence estimates: {hiscox_mturk} percent on MTurk but {hiscox_gfk} percent on [[GfK]]."),
  paste(
    "Table 6.1 lists twelve panel survey experiments and none of them is fielded on Lucid; the",
    "Hiscox rows of table 6.4 are Mechanical Turk and GfK, and table 6.4 gives the zero to GfK.",
    "The two percentages are left at the whole numbers the sentence uses because they come from",
    "a bootstrap the analysis runs without a seed, and a decimal place would state a precision",
    "the estimator does not have."),
  "c6_hiscox_lucid",

  4, "quantity", "pipeline", "full",
  "In the lower half of table 2.3, the difference between the two convincingness ratings for proponents does not equal the difference between the two cells printed above it.",
  "published table 2.3",
  str_glue("The table prints {one_dp(convincing$pro_study)} for the pro-capital punishment study and {one_dp(convincing$anti_study)} for the anti-capital punishment study, and gives their difference as [[3.0]]."),
  str_glue("The difference is [[{one_dp(convincing$difference)}]]."),
  paste("The changed artifact is that single cell; every other cell in both halves of the",
        "table reproduces."),
  "t2_3_gc_cells",

  5, "quantity", "pipeline", "full",
  "Page 101 gives a standard error that disagrees with the book's own appendix table A.5.",
  "published p. 101",
  "As shown in the left facet, the average effect of the two-sided message on support for capital punishment is very close to zero for both proponents (0.28 scale points, SE: 0.18) and opponents (0.10, SE: [[0.11]]).",
  str_glue("As shown in the left facet, the average effect of the two-sided message on support for capital punishment is very close to zero for both proponents (0.28 scale points, SE: 0.18) and opponents (0.10, SE: [[{two_dp(two_sided_se$std.error)}]])."),
  str_glue(
    "Table A.5 reports {two_dp(two_sided_se$std.error)} for this same standard error, and the ",
    "reanalysis reproduces the appendix. The other seven quantities in the passage are correct ",
    "as printed."),
  "c5_twosided_support_opp_se"
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# Every id an entry claims to correct must be a real ground-truth claim. The build gate in
# ground_truth/build_ground_truth.R checks the same property from the other side; checking it
# here too means a dangling id cannot survive a render.
gt_ids <- read_csv(here::here("ground_truth", "coppock_2022_ground_truth.csv"),
                   show_col_types = FALSE)$claim_id
cited_ids <- entries$claim_ids |>
  str_split(";") |>
  unlist() |>
  str_trim() |>
  discard(\(x) is.na(x) | x == "")
stopifnot(all(cited_ids %in% gt_ids))

# The prose below counts the entries in words, as the note has always done.
n_entries_word <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
                    "ten", "eleven", "twelve")[nrow(entries)]

# The spine's markup, resolved for this document.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

`r str_to_title(n_entries_word)` errata in *Persuasion in Parallel: How Information Changes Minds about Politics*
(University of Chicago Press, 2022), <https://doi.org/10.7208/chicago/9780226821832.001.0001>.
None of the `r n_entries_word` changes any conclusion the book draws. Every corrected value below is
computed at render time rather than typed: four of the five from the maintained reanalysis in
`active-maintenance-aec/coppock_2022`, and entry 2 from the book's own printed tables, held in
that repository's transcription of them.

**Provenance.** Every discrepancy below was checked against the printed edition. The
reanalysis itself reads an uncorrected proof dated 26 May 2022, so each quoted sentence was
verified against the published book rather than taken from that file. These are properties of
the book as printed, not of any one rendering of it.

---

```{r}
#| label: entry-1-head
#| echo: false
#| results: asis
# A heading is only a heading when a blank line precedes it, so every emitted block opens
# with one. The two tables beneath are the entry's floats and stay in the document.
e <- entries |> filter(entry == 1)
cat("\n\n**1.** ", e$title, "\n", sep = "")
```

> Change in attitudes toward the death penalty
>
> | | Proponents | Opponents |
> |---|---|---|
> | After **pro**-capital punishment study | `r anti_study("attitude", "Proponents")` | `r anti_study("attitude", "Opponents")` |
> | After **anti**-capital punishment study | `r pro_study("attitude", "Proponents")` | `r pro_study("attitude", "Opponents")` |
>
> Change in beliefs in deterrent efficacy
>
> | | Proponents | Opponents |
> |---|---|---|
> | After **pro**-capital punishment study | `r anti_study("belief", "Proponents")` | `r anti_study("belief", "Opponents")` |
> | After **anti**-capital punishment study | `r pro_study("belief", "Proponents")` | `r pro_study("belief", "Opponents")` |

*Corrected:*

> Change in attitudes toward the death penalty
>
> | | Proponents | Opponents |
> |---|---|---|
> | After **anti**-capital punishment study | `r anti_study("attitude", "Proponents")` | `r anti_study("attitude", "Opponents")` |
> | After **pro**-capital punishment study | `r pro_study("attitude", "Proponents")` | `r pro_study("attitude", "Opponents")` |
>
> Change in beliefs in deterrent efficacy
>
> | | Proponents | Opponents |
> |---|---|---|
> | After **anti**-capital punishment study | `r anti_study("belief", "Proponents")` | `r anti_study("belief", "Opponents")` |
> | After **pro**-capital punishment study | `r pro_study("belief", "Proponents")` | `r pro_study("belief", "Opponents")` |

```{r}
#| label: entry-1-note
#| echo: false
#| results: asis
cat("\n\n", (entries |> filter(entry == 1))$note, "\n", sep = "")
```

---

```{r}
#| label: entry-2-head
#| echo: false
#| results: asis
e <- entries |> filter(entry == 2)
cat("\n\n**2.** ", e$title, "\n", sep = "")
```

Every persistence figure in chapter 6 comes from a bootstrap the deposited code runs without
a seed, so no rerun can settle what these sentences should say. The tables can, and each
corrected figure below is the number the book's own table 6.2 or table 6.3 prints for the same
quantity. The tables are also the side the estimator supports: run at `r c6_seeds` seeds, all
five of the figures the tables print fall inside the range their quantity takes across seeds,
and none of the five figures the prose gives does.

```{r}
#| label: entry-2-body
#| echo: false
#| results: asis
# The four sentences come from the spine, one paragraph each; the page headings stay here,
# because which sentence sits under which page is a fact about the book's pages.
e <- entries |> filter(entry == 2)
pages <- c("*Page 114.*", "*Page 117.*", "", "*Page 118.*")
published_parts <- str_split_1(e$published, "\n\n")
corrected_parts <- str_split_1(e$corrected, "\n\n")
stopifnot(length(published_parts) == length(pages),
          length(corrected_parts) == length(pages))
walk(seq_along(pages), function(i) {
  cat("\n\n", if (pages[i] != "") paste0(pages[i], "\n\n") else "",
      "> ", bold(published_parts[i]), "\n\n*Corrected:*\n\n> ", bold(corrected_parts[i]),
      "\n", sep = "")
})
cat("\n\n", e$note, "\n", sep = "")
```

---

```{r}
#| label: entry-3
#| echo: false
#| results: asis
e <- entries |> filter(entry == 3)
cat("\n\n**3.** ", e$title, "\n\n> ", bold(e$published), "\n\n*Corrected:*\n\n> ",
    bold(e$corrected), "\n\n", e$note, "\n", sep = "")
```

---

```{r}
#| label: entry-4
#| echo: false
#| results: asis
# This entry's published and corrected artifacts are two cells of one table, so the document
# sets them as a sentence rather than as facing blocks.
e <- entries |> filter(entry == 4)
cat("\n\n**4.** ", e$title, "\n\n", bold(e$published), " ", bold(e$corrected), " ", e$note,
    "\n", sep = "")
```

---

```{r}
#| label: entry-5
#| echo: false
#| results: asis
e <- entries |> filter(entry == 5)
cat("\n\n**5.** ", e$title, "\n\n> ", bold(e$published), "\n\n*Corrected:*\n\n> ",
    bold(e$corrected), "\n\n", e$note, "\n", sep = "")
```

```{r}
#| label: emit-spine
#| include: false

# The machine-readable spine, written wherever this document is rendered. Anything else that
# carries these corrections reads it rather than keeping its own copy, so the two cannot drift.
write_csv(entries, here("errata_entries.csv"))
```
