---
title: "Reproduction report: *Persuasion in Parallel* (Coppock 2022)"
format:
  gfm:
    output-file: README.md
    toc: true
  pdf:
    output-file: coppock_2022_report.pdf
    toc: true
    number-sections: true
---

```{r}
#| label: setup
#| include: false
library(here)
library(tidyverse)
library(knitr)
library(kableExtra)

here::i_am("README.qmd")

knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

latex_out <- knitr::is_latex_output()

# value_paper must be read as a character column, or "0.20" becomes 0.2 and the report
# prints a precision the book does not use.
ground_truth <- read_csv(
  here::here("ground_truth", "coppock_2022_ground_truth.csv"),
  col_types = cols(
    value_paper = col_character(),
    value_rewrite = col_character(),
    value_script = col_character(),
    match = col_integer(),
    match_rewrite = col_integer(),
    holds = col_integer(),
    .default = col_character()
  )
)

published_claims <- read_csv(
  here::here("ground_truth", "published_claims.csv"),
  col_types = cols(value_paper = col_character(), digits = col_integer(),
                   needs_block = col_logical(), .default = col_character())
)

float_coverage <- read_csv(here::here("ground_truth", "float_coverage.csv"),
                           show_col_types = FALSE)
archive_status <- read_csv(here::here("ground_truth", "archive_run_status.csv"),
                           show_col_types = FALSE)
appendix_values <- read_csv(here::here("ground_truth", "published_appendix_values.csv"),
                            col_types = cols(.default = col_character()))
published_maintext <- read_csv(here::here("ground_truth", "published_maintext_tables.csv"),
                               col_types = cols(value_paper = col_character(),
                                                .default = col_character()))
seed_dispersion <- read_csv(here::here("ground_truth", "seed_dispersion.csv"),
                            show_col_types = FALSE)
manifest <- read_csv(here::here("original_manifest.csv"), show_col_types = FALSE)
members <- read_csv(here::here("original_members_manifest.csv"), show_col_types = FALSE)
timings <- read_csv(here::here("run_timings.csv"), show_col_types = FALSE)

show_table <- function(df, caption = NULL) {
  if (latex_out) {
    kable(df, booktabs = TRUE, linesep = "", caption = caption) |>
      kable_styling(latex_options = c("striped", "scale_down"))
  } else {
    kable(df, caption = caption)
  }
}

figure_path <- function(stem) {
  file.path("maintained", "output", paste0(stem, if (latex_out) ".pdf" else ".png"))
}
```

*Drafted by Claude Opus 5 under the supervision of Alex Coppock.*

## What this repository is

This repository re-runs the empirical content of *Persuasion in Parallel: How Information
Changes Minds about Politics* (Alexander Coppock, University of Chicago Press, 2022)
against a current R environment, rewrites the analysis in modern idiom, and checks every
number the maintained code produces against the number the book prints.

| Item | Link |
|---|---|
| Book | <https://doi.org/10.7208/chicago/9780226821832.001.0001> |
| Publisher page | <https://press.uchicago.edu/ucp/books/book/chicago/P/bo181475008.html> |
| Replication archive | <https://doi.org/10.7910/DVN/I9GSKI> |

```
coppock_2022/
  download_original.R          fetches and verifies the deposited archive
  run_all.R                    the entry point: sources everything, in order
  original/                    the deposited zip (not redistributed; gitignored)
  original_extracted/          the unpacked deposit (rebuilt on every run; gitignored)
  original_manifest.csv        the deposited file, its size and its published checksums
  original_members_manifest.csv  every member of the zip, by size and checksum
  maintained/                  the rewrite; one script per figure or table
  maintained/output/           everything the rewrite writes
  maintained/in_text_claims.R  the second instrument
  ground_truth/                the extraction, the build, and the comparison
  report/                      the rendered PDF of this document
```

To reproduce: clone the repository, open `coppock_2022.Rproj`, and run

```r
source("run_all.R")
```

`run_all.R` fetches the archive from Dataverse, verifies it, runs all
`r nrow(timings)` analysis scripts, builds the ground truth, prints the in-text claims,
and re-verifies the deposit. It took
`r sprintf("%.1f", sum(timings$seconds) / 60)` minutes on the machine that produced the
committed output; that figure describes one machine on one day and nothing else.

## The book

*Persuasion in Parallel* argues that persuasive information moves the opinions of
opposing groups in the same direction by similar amounts, and that the backlash effects
predicted by motivated reasoning theory are rare. The evidence is 23 survey experiments,
some original, some replications and reanalyses of published studies, reported across
seven chapters and an appendix. Twelve of the experiments carry a panel component that
supports the persistence analysis of chapter 6.

```{r}
#| label: float-inventory
#| include: false
inventory <- float_coverage |>
  count(kind = case_when(
    str_starts(float, "figure_") ~ "figures",
    str_starts(float, "table_a") ~ "appendix tables",
    TRUE ~ "main text tables"
  ))
kind_n <- function(label) inventory$n[inventory$kind == label]
```

The book contains `r nrow(float_coverage)` numbered floats: `r kind_n("figures")` figures,
`r kind_n("main text tables")` tables in the main text, and
`r kind_n("appendix tables")` in the appendix.

### A limitation of this report, stated first

**The only copy of the book available to this repository is the uncorrected proof.** Every
page carries the running foot *Uncorrected Proofs for Review Only*, dated 26 May 2022, and
two running heads still read "Appendix 000" and "Notes to Pages 000-000" where the final
page numbers had not been resolved. Published values in the ground truth are therefore
transcribed from that proof rather than from the printed book.

The discrepancies the pipeline found are properties of the analysis rather than of the
typesetting, so they do not depend on which copy is read, and `errata.qmd` states them with
their corrected values computed at render time. Four of the five were checked against the
printed edition, so none of those is an artifact of the proof or of the way a PDF's text
layer is read. The fifth, errata entry 2, is the set of chapter 6 sentences that disagree
with the chapter 6 tables; it has not had that check, and the errata says so on its face.
Both sides of that disagreement are read from the same copy, so the disagreement is internal
to whichever copy is read, but whether the printed edition carries the same five figures is
open.

No errata page for the book exists on the publisher's site or on the author's own page.

## The deposited archive

The deposit is a single 6 MB zip at <https://doi.org/10.7910/DVN/I9GSKI>, holding
`r sum(str_detect(members$member, "^replication_archive/code/.*\\.R$"))` R scripts,
`r sum(str_detect(members$member, "^replication_archive/data/.*\\.rds$"))` pre-cleaned
`.rds` data files and a README. Because the deposit is a container, `original/` holds one
file and an emptiness check on it would be vacuous, so the repository carries two
manifests: `original_manifest.csv` for the zip and `original_members_manifest.csv` for its
`r nrow(members)` members. `download_original.R` verifies the zip against its published
MD5 and its byte size, refuses to continue if `original/` holds anything the manifest does
not list, audits `original_extracted/` before rebuilding it, rebuilds it from the zip, and
audits it again. `run_all.R` sources that file first and again last, so a script that
wrote into the deposit mid-run is caught at the end of the same run rather than months
later.

The deposited checksum is
`r manifest$md5_served[1]`, and it is the same value Dataverse publishes. Post-run
checksums are not quoted anywhere in this report: a PDF records the time it was written,
so a hash taken after a run can never recur.

### Does the deposited code run?

```{r}
#| label: archive-summary
archive_summary <-
  archive_status |>
  count(pass, status) |>
  pivot_wider(names_from = status, values_from = n, values_fill = 0)
show_table(archive_summary, "Deposited scripts by outcome, as shipped and stripped to data plus code")
```

```{r}
#| label: archive-cause
#| include: false
sunflower_failures <- sum(str_detect(archive_status$message, "unused arguments") &
                            archive_status$pass == "as_shipped", na.rm = TRUE)
n_scripts <- nrow(archive_status) / 2
```

No. `r n_scripts - sum(archive_status$status == "ok" & archive_status$pass == "as_shipped")`
of the `r n_scripts` deposited analysis scripts fail, and
`r sunflower_failures` of them fail on one line for one reason: `vayr::sunflower()`
replaced its `width` and `height` arguments with `density` and `aspect_ratio`, so every
call in the deposit raises `unused arguments`. Since almost every figure in the book is a
sunflower plot, that single API change takes down most of the archive. The remaining
failure is `figure_3.1.R`, which dies inside `ggbrace::geom_brace()`.

The stripped-copy test is vacuous for this deposit and is recorded as such rather than
reported as a pass: the archive ships 21 pre-cleaned `.rds` files and no derived object
produced by its own code, so the stripped and as-shipped copies hold the same inputs and
return the same per-script outcome.

The deposit writes nothing. There is no `ggsave()`, no `pdf()`, no `write_csv()` and no
`png()` anywhere in its 30 scripts; the figures are drawn to the active device and the
tables are printed to the console with `print.xtable()`. Running it therefore overwrites
zero deposited files, and that measured zero has an explanation rather than being left to
speak for itself: most scripts fail before reaching anything, and the ones that succeed
have nothing to write. One stray file appears, an `Rplots.pdf` that `Rscript` leaves
behind.

### Why `value_script` is empty

The ground truth's archive column is empty on every row, and that is a finding rather than
an omission. Twenty-three scripts never reach a value. Of the five that run, three print
nothing at all, and the two that do print (the chapter 6 table scripts) call
`rsample::bootstraps()` with no seed, so what they print changes from run to run and could
not honestly be committed as a property of the deposit.

## Chapter 6 is unseeded

Neither of the deposit's two chapter 6 scripts sets a seed. Every number in tables 6.2,
6.3 and 6.4, in figures 6.1 and 6.2, and in the persistence sentences of chapter 6 is one
draw of an unseeded bootstrap. The bootstrap reaches the point estimates as well as the
standard errors, which is easy to miss: `metafor::rma()` weights each study by the inverse
of its squared standard error, and those standard errors are the bootstrapped ones.

`ground_truth/measure_seed_dispersion.R` re-runs both scripts across
`r max(seed_dispersion$n_seeds)` seeds and records how far each published quantity could
have landed. Rows that depend on it carry `match_rewrite = NA` with the verdict in
`holds`, compared against the range rather than against a single number.

```{r}
#| label: dispersion
show_table(
  seed_dispersion |>
    transmute(Float = float, Quantity = quantity,
              Minimum = sprintf("%.3f", minimum),
              Median = sprintf("%.3f", median),
              Maximum = sprintf("%.3f", maximum)),
  "Range of each chapter 6 quantity across seeds"
)
```

## The extraction and the two instruments

`ground_truth/published_claims.csv` is the extraction: every claim the comparison covers,
with the location in the book that states it, its type, the string the page prints, and
the number of decimals it prints at. It carries `r nrow(published_claims)` rows, of which
`r sum(published_claims$needs_block)` are prose claims that must have a block in
`maintained/in_text_claims.R` and `r sum(!published_claims$needs_block)` are float-level
rows reading cells-reproduced-of-cells.

Two instruments reach the same claimed numbers by separate paths from the same pipeline
outputs:

- `ground_truth/build_ground_truth.R` joins each published value to what
  `maintained/output/` contains and writes `coppock_2022_ground_truth.csv`.
- `maintained/in_text_claims.R` carries the book's sentence verbatim beside code that
  recomputes the number, and prints `CLAIM <id> = <value> || <label>`.

Where a second derivation exists the claims file takes it: the chapter 1 treatment effects
are recovered there by differencing the two condition means the figure plots, and the
chapter 5 correlations by recomputing them from the plotted pairs, rather than by reading
back the same file the build reads.

The gate in `build_ground_truth.R` runs the claims file non-interactively under
`capture.output()`, in its own environment, and asserts that the number of printed claim
ids equals the number of required blocks, that every required id is printed, that no
printed id is undeclared, and that the value each block printed equals the value the build
rendered. A separate check re-renders each published string at the digit count the
extraction records and requires it to equal the string stored, so a shared `digits` column
cannot make the two instruments agree about a precision that is wrong.

The gate was tested by breaking it rather than by reading it. Deleting a block fails the
count; changing a value in a block fails the cross-instrument comparison; changing a
`digits` entry fails the precision check.

### What the extraction does not cover

The extraction covers the numeric claims of chapters 1 through 6 and every float in the
book. It deliberately excludes three classes, each for a reason that was checked rather
than assumed:

- The appendix reproduces the full text of five newspaper op-eds and the wording of every
  treatment and outcome used in the 23 experiments. Those pages are dense with numbers
  ("$9 billion in debt", "14.5% flat tax", "8 of the 10 pairs"), and every one is
  transcribed from a source outside the book. They cannot drift and nothing in the
  pipeline could check them.
- Chapters 3, 4 and 7 contain worked illustrations: a hypothetical 3-point and 5-point
  effect, a power calculation returning 3,000 subjects, a simulated subject with ten
  considerations, and a run of Bayes' rule arithmetic. These are definitional, and each is
  verified where it is used rather than against a pipeline that never computes them.
- Tables 2.1 and the upper half of table 2.3 reproduce Lord, Ross, and Lepper's own
  tables 3 and 1 from 1979. They are transcriptions, checked once against that article.

## Ground truth

```{r}
#| label: gt-summary
verdicts <-
  ground_truth |>
  transmute(
    verdict = case_when(
      !is.na(match_rewrite) & match_rewrite == 1 ~ "Matches at the book's precision",
      !is.na(match_rewrite) & match_rewrite == 0 ~ "Does not match",
      !is.na(holds) & holds == 1 ~ "Holds (no printed value to match)",
      !is.na(holds) & holds == 0 ~ "Does not hold",
      TRUE ~ "No verdict (approximate, or nothing computed)"
    )
  ) |>
  count(verdict, name = "Rows") |>
  rename(Verdict = verdict)
show_table(verdicts, "Ground truth verdicts")
```

```{r}
#| label: gt-adverse
adverse <-
  ground_truth |>
  filter((!is.na(match_rewrite) & match_rewrite == 0) | (!is.na(holds) & holds == 0)) |>
  transmute(Claim = claim, Book = value_paper, Locus = defect_locus)
show_table(adverse, "Every row that does not agree")
```

### Float coverage

```{r}
#| label: coverage
covered_values <- sum(float_coverage$covered[float_coverage$published > 0])
published_values <- sum(float_coverage$published)
zero_coverage <- float_coverage |> filter(published > 0, covered == 0)
```

Across the book's `r nrow(float_coverage)` floats the pipeline reproduces
`r format(covered_values, big.mark = ",")` of
`r format(published_values, big.mark = ",")` published values. The fraction is stated for every float that
prints one, because an aggregate hides a float covered by a single row:

```{r}
#| label: coverage-per-float
show_table(
  float_coverage |>
    filter(published > 0) |>
    transmute(Float = float, `Published values` = published, Reproduced = covered,
              Fraction = sprintf("%.0f%%", 100 * covered / published)),
  "Published values reproduced, by float"
)
```

`r nrow(zero_coverage)` published floats have zero coverage, and each has a reason that was
tested:

```{r}
#| label: coverage-zero
show_table(
  zero_coverage |>
    transmute(
      Float = float,
      `Published values` = published,
      Reason = c(
        "table_4.2" = "Sample sizes for the 23 experiments. The deposit computes none of them and neither does the rewrite.",
        "table_6.1" = "Panel sample sizes for the 12 persistence experiments, on the same footing as table 4.2.",
        "table_a.1" = "The deposit contains no code for the Coppock, Ekins, and Kirby treatment effect estimates.",
        "table_a.8" = "The deposit contains no code for the Hiscox treatment effect estimates."
      )[float]
    ),
  "Published floats with no coverage"
)
```

The reason given for tables A.1 and A.8 is a measurement rather than an impression. The
deposit contains thirteen `print.xtable()` calls; eleven build appendix tables and two
build the chapter 6 tables, and none of the thirteen builds A.1 or A.8. A reconstruction
of A.8 from the deposited data reproduces its valence contrasts and not all of its expert
contrasts, which is why the specification is treated as unrecoverable rather than guessed
at.

```{r}
#| label: figure-coverage
#| include: false
figure_rows <- float_coverage |> filter(str_starts(float, "figure_"))
plotted_estimates <- sum(figure_rows$covered)
drawn_figures <- sum(figure_rows$covered > 0)
```

The `r kind_n("figures")` figures print no estimates on their faces, so they contribute
nothing to the counts above. Every one is a scatter of individual responses with condition
means and intervals drawn over it, so what a figure asserts is the set of estimates it
plots, and each figure script writes those estimates to a CSV:
`r format(plotted_estimates, big.mark = ",")` estimates across the `r drawn_figures`
figures the rewrite draws. Seven figures have no such file: figure 1.1 and figures 4.1, 4.2
and 7.1 are schematics and simulations with no data behind them, figure 2.1 reproduces two
graphics used as experimental stimuli, figure 3.4 is a diagram, and figure 5.14 reproduces
the two income-inequality plots that are themselves the Trump and White treatment.

### The appendix

`ground_truth/published_appendix_values.csv` holds every cell of the book's 14 appendix
estimate tables, `r nrow(appendix_values) * 4` published numbers in
`r nrow(appendix_values)` rows, parsed positionally from the page. Positional parsing is
not a preference here: read in reading order, `pdftotext` loses the numeric columns of
table A.2 entirely and returns a table that looks complete and is not. Three artifacts of
this PDF each drop rows if unhandled: a negative number is typeset as a minus sign
followed by a soft hyphen and sometimes a space, the minus sign is U+2212 rather than a
hyphen, and the small-capital T of "Table" is dropped from table A.10's caption.

## Errata

```{r}
#| label: errata-values
#| include: false
convincing <- read_csv(here::here("maintained", "output", "table_2.3_gc_replication.csv"),
                       show_col_types = FALSE) |>
  filter(rating == "convincing", str_detect(predisposition, "Proponents"))
```

Nine sentences, labels or cells in the book do not survive the reanalysis, in five entries.
They are set out in `errata.qmd`, rendered to `coppock_2022_errata.pdf` at the repository
root, with every corrected value computed at render time: from `maintained/output/` where
the reanalysis settles it, and from the book's own transcribed tables where the estimator
behind it is unseeded. Summarized here:

**1. Table 2.2's two study rows carry each other's labels, in both panels.** The cells
printed under "After pro-capital punishment study" are the means among subjects who read
the anti-capital punishment study, and the reverse. Three artifacts identify which row is
which and all three agree: the content variable in the deposited data, figure 2.2 drawn
from that same variable, and the sentence on page 26 reporting that self-assessed change is
higher in the pro condition than in the null and higher in the null than in the con. The
values are correct and are printed in the order the analysis produces them; the "Combined"
rows are sums and are unaffected, which is why the reading the surrounding text draws from
the table is unchanged.

**2. Four sentences in chapter 6 report persistence figures that the chapter's own tables
print differently.** Page 114 gives the weaker persistence group as 20 per cent where table
6.2 prints 0.21; page 117 gives the op-ed effects as 46 per cent after ten days and 44 after
thirty where table 6.3 prints 0.48 and 0.46; page 118 gives 57 per cent for Republicans and
43 for Democrats after ten days where table 6.3 prints 0.53 and 0.48. Every persistence
figure in the chapter comes from a bootstrap the deposit runs without a seed, so no rerun
settles what the sentences should say. The tables do, and they are also the side the
estimator supports: every figure the tables print is inside the range its quantity takes
across seeds, and every figure the prose gives is outside it.

```{r}
#| label: chapter-6-prose
chapter_6_prose <- tribble(
  ~claim_id,                ~sentence,                              ~float,      ~panel,     ~row_label,                         ~quantity,
  "c6_persistence_weaker",  "p. 114, weaker persistence group",     "table_6.2", "estimate", "Prediction: weaker persistence",   "Prediction: weaker persistence",
  "c6_oped_ten_days",       "p. 117, op-eds after ten days",        "table_6.3", "10 days",  "Overall",                          "Overall, 10 days",
  "c6_oped_thirty_days",    "p. 117, op-eds after thirty days",     "table_6.3", "30 days",  "Overall",                          "Overall, 30 days",
  "c6_oped_rep_ten_days",   "p. 118, Republicans after ten days",   "table_6.3", "10 days",  "Republican",                       "Republican, 10 days",
  "c6_oped_dem_ten_days",   "p. 118, Democrats after ten days",     "table_6.3", "10 days",  "Democrat",                         "Democrat, 10 days"
) |>
  left_join(published_claims |> select(claim_id, value_paper), by = "claim_id") |>
  left_join(published_maintext |> select(float = table, panel, row_label, in_table = value_paper),
            by = c("float", "panel", "row_label")) |>
  left_join(seed_dispersion, by = c("float", "quantity"))
stopifnot(nrow(chapter_6_prose) == 5, !any(is.na(chapter_6_prose$in_table)))

show_table(
  chapter_6_prose |>
    transmute(
      Sentence = sentence,
      `In the text` = sprintf("%.0f%%", as.numeric(value_paper)),
      `In its own table` = sprintf("%.0f%%", 100 * as.numeric(in_table)),
      `Across seeds` = sprintf("%.0f%% to %.0f%%", 100 * minimum, 100 * maximum)
    ),
  "Chapter 6 prose against the chapter 6 tables"
)
```

The "In its own table" column is the correction the errata prints. It is not recomputed,
which is the one thing the unseeded estimator forbids; it is the figure the book's own table
already carries, and it comes from the transcription in
`ground_truth/published_maintext_tables.csv` rather than from a run.

**3. Page 114 attributes a persistence estimate to a sample that is not in the analysis.**
The sentence reads "the different replications of the Hiscox (2006) 'expert' treatment
generated very different persistence estimates: 49 percent on MTurk but 0 percent on
Lucid." No Lucid sample appears anywhere in the persistence analysis. Table 6.1 lists
twelve panel experiments and the Hiscox rows of table 6.4 are Mechanical Turk and GfK. The
book's own table 6.4 gives the zero to GfK, and the pipeline reproduces it there.

**4. Table 2.3 contradicts itself.** In the lower half, the mean rating of how convincing
the two studies were is `r sprintf("%.1f", convincing$pro_study)` for the pro-capital
punishment study and `r sprintf("%.1f", convincing$anti_study)` for the anti-capital
punishment study among proponents, and the table prints both. It prints their difference
as 3.0, where the two cells differ by
`r sprintf("%.1f", convincing$difference)`. Every other cell of that half reproduces.

**5. Page 101 disagrees with appendix table A.5.** The sentence gives the standard error of
the two-sided message's effect on capital punishment support among opponents as 0.11.
Table A.5 gives 0.12 for the same quantity, and the pipeline reproduces the appendix.

Three further discrepancies were examined and are not errata. First, the Democratic slope
in the gay marriage series is 2.02 points per year, which prints 2.0 where page 11 says 2.1; the
other three slopes that sentence names reproduce exactly, and a single slope off by a
tenth in a sentence whose point is that the slopes are similar does not mislead a reader
who quotes it. Second, the standard error of the flat tax effect among Republican policy
professionals is 0.24453 under HC2, which prints 0.24 against a published 0.25; under HC3
it is 0.24589 and prints 0.25, and HC3 reproduces all eight of that chapter's standard
errors where HC2 reproduces seven. The deposit contains no code for any of the eight, so
the variance estimator behind the published figure cannot be established, and the rewrite
keeps the house default rather than the one that happens to match. Third, page 114 says the
pro-minimum wage videos, the flat tax op-ed and the pro-capital punishment studies "all had
persistence ratios above 60 percent". Those three treatments span four rows of table 6.4,
because the flat tax op-ed was fielded on two samples and the sentence names neither. Three
of the four clear 60 per cent; the flat tax op-ed among policy professionals is 39 per cent
in the book's own table 6.4 and 39 per cent here. The sentence holds on Mechanical Turk,
where all three treatments were run, so what is wrong is not a number but the absence of
one word, and the ground truth records it as unresolved.

## The maintained rewrite

`maintained/` holds `r nrow(timings)` analysis scripts and a `helpers.R`, one script per
figure, with an appendix table folded into the figure script that shares its model where
the two are inseparable. Every script sources `helpers.R` first and loads no packages of
its own. Paths go through `here::here()`. Output goes to `maintained/output/`, which is
committed so a reader can diff a fresh run against it.

The substitutions the current environment forced:

| Deposit | Rewrite | Why |
|---|---|---|
| `vayr::sunflower(x, y, width, height)` | `sunflower_compat()` | vayr 1.0.0 replaced the two semi-axis arguments with `density` and `aspect_ratio`; the helper inverts the new API's own formulas so the deposit's layout is recovered exactly |
| `do(tidy(...))` | `reframe(tidy(...))` | `do()` is superseded |
| `melt()` / `dcast()` | `pivot_longer()` / `pivot_wider()` | reshape2 is superseded |
| `geom_errorbar(width = 0)` | `geom_linerange()` | house style for interval bars |
| `xtable()` + `print.xtable()` | `write_csv()` | a table printed to the console cannot be diffed |
| `rmeta::meta.summaries()` | `metafor::rma()` | unmaintained since 2018, and its non-standard evaluation fails inside `reframe()` |
| `haven_labelled` outcome | `haven::zap_labels()` | `sunflower()` cannot do arithmetic on a labelled vector |

Six defects in this repository's own code were found by the comparison and fixed:

- Its Brader, Valentino, and Suhay appendix table (A.7) filtered independents out of the
  data at load, so the pooled "Overall" rows were fitted on Democrats and Republicans
  alone. The deposit filters them from the printed rows and not from the sample. All 13
  affected cells now reproduce.
- Its figure 5.16 script computed the six correlations chapter 5 quotes with six bare
  `with(...)` calls at the top level, which print nothing when a file is sourced and wrote
  nothing. The figure's headline quantities had no committed output at all.
- Its figure 2.3 script carried a comment saying table 2.3 reports only the original 1979
  study and could not be produced. Half of that was false: the deposited data carry the
  replication's own quality and convincingness ratings, and computing them is what
  surfaced the contradiction in that table.
- `ground_truth/run_archive.R` described every clean script as having exited non-zero,
  because `tibble()` evaluates its arguments in order and a `status` column shadowed the
  exit code the next argument read.
- `ground_truth/build_ground_truth.R` normalized signed zero on the rewrite's side of the
  appendix comparison and not on the book's, so the two appendix cells the book prints as
  `-0.00` were counted as failures against a rewritten `0.00`.
- Its figure 5.3 script scattered the raw responses of two panels with an unseeded
  `runif()`, following the deposit, so the figure was different on every run while its
  estimates were not. The run-twice diff is what surfaced it, and it is the only file in
  `maintained/output/` that was ever not byte-reproducible.

## Verification

### The figures

```{r}
#| label: fig-1-2
#| fig-cap: "Figure 1.2, the flat tax op-ed experiment, as the rewrite draws it."
knitr::include_graphics(figure_path("figure_1.2_flat_tax_immediate"))
```

```{r}
#| label: fig-5-16
#| fig-cap: "Figure 5.16, conditional average treatment effects across subgroups, as the rewrite draws it."
knitr::include_graphics(figure_path("figure_5.16_cate_correlations"))
```

Every rendered figure was laid beside the published page. The check is not redundant with
the numeric one: a transposed axis or a swapped facet leaves every estimate correct and
every value comparison passing. All `r drawn_figures` reproduced figures match the
published layout, including the facet order and the direction of every axis.

### The pipeline

`run_all.R` was run to completion from clean sessions and the whole of `maintained/output/`
diffed between runs. Every CSV and PNG comes back byte-identical, as does
`ground_truth/coppock_2022_ground_truth.csv`. The figure PDFs differ, and only in their
embedded `CreationDate` and `ModDate`, which a PDF records on every write.

The one thing this check found is worth naming, because it is exactly what the check is
for: figure 5.3 came back different on the second run. Its estimates were identical and its
CSV was byte-identical; what moved was the position of the faint background points in two
of its four panels, scattered by an unseeded `runif()`. Nothing in the numeric comparison
could have seen it.

## R environment

```{r}
#| label: session
show_table(
  tibble(
    Component = c("R", "tidyverse", "estimatr", "metafor", "vayr", "ggplot2", "rsample"),
    Version = c(
      paste(R.version$major, R.version$minor, sep = "."),
      as.character(packageVersion("tidyverse")),
      as.character(packageVersion("estimatr")),
      as.character(packageVersion("metafor")),
      as.character(packageVersion("vayr")),
      as.character(packageVersion("ggplot2")),
      as.character(packageVersion("rsample"))
    )
  ),
  "Environment the committed output was produced under"
)
```

## Licence

CC0 1.0, matching the deposit.
